---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(sjPlot) # for table visualization
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario



# Read data

```{r}
larvae <- read_csv("Data/plank_larvae.csv", trim_ws = TRUE)
```

## Glimpse data and find columns of interest

```{r}
larvae  %>% glimpse()
```

We are interested in Species, Larvae, Initial, Individual, Survivorship, Time

## Isolate variables of interest and data preparation

```{r}
larvae2 <- 
  # old dataframe
  larvae %>% 
  # select relevant columns
  select(Species, 
         Larvae,
         Individual,
         Survivorship,
         Initial,
         Time) %>% 
  # only have data where feeding trials were conducted in daylight hours
  filter(Time == "Day") %>%
  # change Species, Larvae as factors
  mutate(Species = as.factor(Species),
         Larvae = as.factor(Larvae),
         Individual = as.factor(Individual)) %>% 
  mutate(Species = recode(Species,
                          'cur' = 'A. cura',
                          'ret' = 'D. reti',
                          'sex' = 'A. sex',
                          'tri' = 'D. tri',
                          'viri'= 'C. viri')) %>% 
  mutate(Larvae = recode(Larvae,
                         'millepora' = 'A. mill',
                         'heliopora' = 'H. coer')) %>% 
  mutate(survival_prop = Survivorship/Initial)
```

# Exploratory data analysis

```{r}
# scatterplot
larvae2 %>% 
  ggplot(aes(y = Survivorship, x = Larvae)) +
  geom_boxplot() +
  facet_grid(~ Species) +
  theme_classic()
```

Heliopora consistently has higher survivorship compared to A. millepora. We should be able to run an additive model since an interaction term doesn't seem to be present.  

# Fit the model (binomial distribution)

```{r}
larvae_binom_mod <- 
  glmmTMB(survival_prop ~ Larvae + 
            Species +
            (1 | Individual),
        weights = Initial,
        family = binomial(), 
        data = larvae2,
        REML = TRUE)
```

## Model validation

```{r}
larvae_binom_mod  %>% testUniformity()
larvae_binom_mod  %>% plotResiduals() # some minor issues with residuals
larvae_binom_mod %>% testDispersion() # show signs of overdispersion
```

Fit could be better. Let's try betabinomial. 

# Fit model 2 (beta binomial)

```{r}
larvae_bbinom_mod <- 
  glmmTMB(survival_prop ~ Larvae + 
            Species +
            (1 | Individual),
        weights = Initial,
        family = betabinomial(), 
        data = larvae2,
        REML = TRUE)
```

## Model validation

```{r}
larvae_bbinom_mod %>% testUniformity() # qqplot
larvae_bbinom_mod %>% plotResiduals() # residual plot
larvae_bbinom_mod %>% testDispersion()
```

Dispersion still seems to be an issue, but we are somewhat out of options and it doesn't seem to be too bad. 

## Predictions / emmeans

```{r}
# grid preparation
larvae_newdata <-
  larvae_bbinom_mod %>% 
  emmeans(~ Larvae + Species,
          type = "response") %>% 
  as.tibble()

larvae_newdata %>% head()
```

## Plot

```{r}
p_larvae <-
larvae_newdata %>% 
  ggplot(aes(y = prob, 
             x = Species, 
             fill = Larvae, 
             color = Larvae,
             shape = Larvae)) +
  geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
                  position = position_dodge(0.5)) +
  scale_x_discrete(name = "Fish species") +
  scale_y_continuous(name = "Proportional larvae survivorship",
                     limits = c(0,1),
                     breaks = seq(0,1, by = 0.2)) +
  theme_classic() +
  ggtitle("a)")
```

## Model interpretation

```{r}
larvae_bbinom_mod %>% broom.mixed::tidy(
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = TRUE # in log odds ratio
)
```

Survivorship of Acropora overall is 91% lower when compared to Heliopora.
Survivorship of larvae varies with fish species when held at Heliopora only

## Pairwise comparisons

Let us say we want to know differences in survivorship of Heliopora or Acropora among fish species. 

### Pairwise between fish species on similar larvae

```{r}
# comparisons betweem min, 50m, 75m, and max depth
pairwise_larvae <- 
larvae_bbinom_mod |> 
  emmeans(~Species | Larvae,
          epred = TRUE) |> 
  pairs(type = "link") %>% 
  as.tibble()

pairwise_larvae %>% head()
```

### Plot

```{r}
p_pairwise_larvae <-
pairwise_larvae  %>% 
  mutate(contrast = fct_rev(fct_inorder(contrast))) %>% 
  ggplot(aes(y = contrast, x = estimate)) +
  geom_point() +
  geom_pointrange(aes(x = estimate, xmax = estimate + SE, xmin = estimate - SE)) +
  geom_vline(xintercept = 0, lty = 11, color = "red") +
  scale_x_continuous("Contrast ratio (log-scale)",
                     limits = c(-2,2)) +
  scale_y_discrete("") +
  ggtitle("b) Comparisons among fish species") +
  theme_classic() 
```

# Combine plot

```{r}
p_final_larvae <- 
p_larvae / p_pairwise_larvae 
```

# Save plot

```{r}
ggsave("Figures/Fig_betabinom_Larvae.jpeg",
       plot = p_final_larvae,
       dpi = 300,
       height = 6,
       width = 6,
       units = "in")
```