---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2025) investigated changes in species richness with depth in the Coral Sea, Australia. To do so, we used ROV surveys across a depth range of 2-98 throughout 50 sites. Each ROV survey lasted for 2.5 mins and covered an estimated area of about 30m per survey.

# Read data

```{r}
nutri <- read_csv("Data/tile_nutrients.csv", trim_ws = TRUE)
```

## Glimpse data and find columns of interest

```{r}
nutri %>% glimpse()
```

We are interested in Nitrate,  Site

## Isolate variables of interest and data preparation

```{r}
nutri2 <- 
  # old dataframe
  nutri %>% 
  # select relevant columns
  select(Site, 
         Phosphate) %>% 
  # change Site as factor
  mutate(Site = factor(Site,
                    levels = c("Tomasa",
                    "Lucero",
                    "Malilnep")))

nutri2 %>% head()
```

# Exploratory data analysis

```{r}
# boxplot
nutri2 %>% 
  ggplot(aes(y = Phosphate, x = Site)) +
  geom_boxplot() +
  theme_classic()
```

# Fit the model 1 (gaussian distribution)

This assumes no site level variance (i.e. a simple glm)

```{r}
nutri_gau_mod <- 
  glmmTMB(Phosphate ~ Site,
        family = gaussian(link = 'identity'), 
        data = nutri2,
        REML = TRUE)
```

## Model validation

```{r}
nutri_gau_mod %>% testUniformity() # qqplot
nutri_gau_mod %>% plotResiduals() # residual plot
```

Fit looks good

# Save / load model

```{r}
save(nutri_gau_mod, file = "Model_Outputs/nutri_gau_mod.RData")

load("Model_Outputs/nutri_gau_mod.RData")
```

## Predictions / emmeans

```{r}
phos_newdata <-
  nutri_gau_mod  %>% 
  emmeans(~ Site,
          type = "response") %>% 
  as.tibble()

phos_newdata %>% head()
```

## Plot

```{r}
p_phos <-
phos_newdata %>% 
  ggplot(aes(y = emmean, x =Site)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
              fill = "#8AA17D",
              alpha = 0.3) +
  scale_x_discrete(name = "Site") +
  scale_y_continuous(name = "Phosphate concentrations",
                     limits = c(0.2,1),
                     breaks = seq(0.2,1, by = 0.2)) +
  theme_classic() +
  ggtitle("a)")
```

## Model interpretation

```{r}
nutri_gau_mod %>% broom.mixed::tidy(
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = FALSE) %>% 
  mutate(p.value = round(p.value, 3))
```

Site influenced phosphate concentrations but only when Tomasa (reference group) was compared to Lucero and Malilnep where concentrations were 0.21 uM lower. However, what about Lucero vs Malilnep?

## Pairwise comparisons

```{r}
pairwise_nutri <- 
nutri_gau_mod |> 
  emmeans(~ Site, 
          epred = TRUE) |> 
  pairs() %>%
  summary(infer = c(TRUE, TRUE), # return pvalue and conf
          level = 0.95) %>% 
  as.tibble()

pairwise_nutri %>% head()
```

### Plot

```{r}
p_phos_pairwise <-
pairwise_nutri  %>% 
mutate(contrast = fct_rev(fct_inorder(contrast))) %>% 
ggplot(aes(y = estimate, x = contrast)) +
  geom_point() +
  geom_pointrange(aes(y = estimate, ymax = lower.CL, ymin = upper.CL)) +
  geom_hline(yintercept = 0, lty = 11, color = "red") +
  scale_y_continuous("Contrast ratio") +
  scale_x_discrete("") +
  theme_classic() +
  ggtitle("b)")
```

# Combine plot

```{r}
p_final_phos <- 
p_phos / p_phos_pairwise
```

# Save plot

```{r}
ggsave("Figures/Fig_gau_Phos.jpeg",
       plot = p_final_phos,
       dpi = 300,
       height = 5,
       width = 5,
       units = "in")
```
