---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(sjPlot) # for table visualization
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2025) investigated changes in species richness with depth in the Coral Sea, Australia. To do so, we used ROV surveys across a depth range of 2-98 throughout 50 sites. Each ROV survey lasted for 2.5 mins and covered an estimated area of about 30m per survey.

# Read data

```{r}
spr <- read_csv("Data/herb_sprich.csv", trim_ws = TRUE)
```

## Glimpse data and find columns of interest

```{r}
spr %>% glimpse()
```

We are interested in Site, Depth_m, Estimator

## Isolate variables of interest and data preparation

```{r}
spr2 <- 
  # old dataframe
  spr %>% 
  # select relevant columns
  select(Estimator, 
         Depth_m,
         Site) %>% 
  # change Site as factor
  mutate( Site = as.factor(Site)) %>% 
  # rename Estimator to SRich for ease
  rename(SRich = Estimator)
```

# Exploratory data analysis

```{r}
# scatterplot
spr2 %>% 
  ggplot(aes(y = SRich, x = Depth_m)) +
  geom_point() +
  geom_smooth()

historgram
  spr2 %>% 
  ggplot(aes(x = SRich)) +
  geom_histogram()
```

# Fit the model 1 (gaussian distribution)

This assumes no site level variance (i.e. a simple glm)

```{r}
spr_gau_mod <- 
  glmmTMB(SRich ~ Depth_m,
        family = gaussian(link = 'identity'), 
        data = spr2,
        REML = TRUE)
```

## Model validation

```{r}
spr_gau_mod %>% testUniformity() # qqplot
spr_gau_mod %>% plotResiduals() # residual plot
```

Here we can see that our fit is garbage, so we need to reevaluate our models

# Fit the model 2 (lognormal)

This assumes no site level variance (i.e. a simple glm)

```{r}
spr_ln_mod <- 
  glmmTMB(SRich ~ Depth_m,
        family = lognormal(), 
        data = spr2,
        REML = TRUE)
```

## Model validation

```{r}
spr_ln_mod %>% testUniformity() # qqplot
spr_ln_mod %>% plotResiduals() # residual plot
```

This model is def better than model 1. We get some warnings but the shape of the residual plot doesn't seem to follow any shape (i.e. it is within an acceptable range of error).

Now let's try including a random variable (i.e. a glmm before we )

# Fit model 3 (include site as random variable)

```{r}
spr_lnr_mod <- 
  glmmTMB(SRich ~ Depth_m +
            (1 | Site),
        family = lognormal(), 
        data = spr2,
        REML = TRUE)
```

## Model validation

```{r}
spr_lnr_mod %>% testUniformity() # qqplot
spr_lnr_mod %>% plotResiduals() # residual plot
```

# Save / load model

```{r}
save(spr_lnr_mod, file = "Model_Outputs/spr_lnr_mod.RData")

load("Model_Outputs/spr_lnr_mod.RData")
```

## Predictions / emmeans

```{r}
# Prepare matrix for predicted data to be stored
spr_grid <- with(spr2,
                    data.frame(Depth_m = seq(min(Depth_m),
                                             max(Depth_m),
                                             length = 100)))

# emmeans
spr_newdata <- spr_lnr_mod %>% 
  emmeans(~ Depth_m, 
          at = spr_grid,
          type = 'response') %>% # change data from log to response scale
  as.data.frame()

#spr_newdata %>% head()
```

## Plot

```{r}
p_sprdepth <-
spr_newdata %>% 
  ggplot(aes(y = response, x =Depth_m)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              fill = "#8AA17D",
              alpha = 0.3) +
  geom_line() +
  scale_x_continuous(name = "Depth") +
  scale_y_continuous(name = "Species richness",
                     limits = c(0,10),
                     breaks = seq(0,10, by = 2)) +
  theme_classic() +
  ggtitle("a)") +
  geom_image(data = tibble(Depth_m = 70,
                            response = 9),
                            aes(image = ("Images/naso.png")),
                            size = 0.30)
```

## Model interpretation

```{r}
spr_lnr_mod %>% broom.mixed::tidy(
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = TRUE
)
```

Depth has a negative effect on species richness of herbivores. The rate of decrease is 1.2% (1 - 0.988 in the estimate) for every m change in depth. The probability of this not happening due to chance is \< 0.001 and suggest a significant effect of depth.

## Pairwise comparisons

Let us say we want to know differences in species richness between the shallowest and maximum depth. We can do so with pairwise contrasts.

### Extract min and max values

```{r}
min_max_depth <- spr2 %>% 
  summarise(min_depth = min(Depth_m),
            max_depth = max(Depth_m)) %>% 
  unlist(use.names = FALSE) %>% # remove column names of min and max depth
  as_tibble() %>% # have them as one column
  rename(Depth_m = value) # name column as Depth_m
```

### Pairwise between shallowest and deepest depth

```{r}
# comparisons from 2.3 to 98m
pairwise_spdepth <- 
spr_lnr_mod |> 
  emmeans(~ Depth_m, 
          at = min_max_depth, 
          epred = TRUE) |> 
  pairs(type = "response") %>%
  confint(level = 0.95) %>% 
  as.tibble()
# 3x more herbivores in the shallowest compared to the deepest
# can also be presented as a 202% (3.02 - 1) increase in richness from deep to shallow

# [inverse] comparisons from 98 to 2.3m
spr_lnr_mod |> 
  emmeans(~ Depth_m, 
          at = min_max_depth, 
          epred = TRUE) |> 
  pairs(rev = TRUE, 
        type = "response") %>% 
    confint(level = 0.95) %>% 
  as.tibble()
# 66% lower herbivores in the deepest compared to the shallowest depth band
```

### Plot

```{r}
p_sp_pairwise <-
pairwise_spdepth %>% 
ggplot(aes(y = ratio, x = contrast)) +
  geom_point() +
  geom_pointrange(aes(y = ratio, ymax = asymp.LCL, ymin = asymp.UCL)) +
  geom_hline(yintercept = 1, lty = 11, color = "red") +
  scale_y_continuous("Contrast ratio") +
  scale_x_discrete("") +
  theme_classic() +
  ggtitle("b)")
```

# Combine plot

```{r}
p_final_spr <- 
p_sprdepth + p_sp_pairwise
```

# Save plot

```{r}
ggsave("Figures/Fig_Ln_Spr_Depth.jpeg",
       plot = p_final_spr,
       dpi = 300,
       height = 4,
       width = 6,
       units = "in")
```
