---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Data is from Tim and colleagues (2025) and has the same descriptions as the gaussian and lognormal models so I won't be elaborating again here.

# Read data

```{r}
abun <- read_csv("Data/herb_abundance.csv", trim_ws = TRUE)
```

## Glimpse data and find columns of interest

```{r}
abun  %>% glimpse()
```

We are interested in Reef_2, Site, Depth_m, cropper, browser, detritivore, excavator, scraper

## Isolate variables of interest and data preparation

```{r}
abun2 <- 
  # old dataframe
  abun %>% 
  # select relevant columns
  select(Reef_2, 
         Site,
         Depth_m,
         cropper,
         browser,
         detritivore,
         excavator,
         scraper) %>% 
  # change Reef_2, Site as factors
  mutate(Reef_2 = as.factor(Reef_2),
         Site = as.factor(Site)) %>% 
  # combine all herbivore feeding groups as "All_herbs"
  mutate(All_herbs = cropper + browser + detritivore + excavator + scraper)
```

# Exploratory data analysis

```{r}
# scatterplot
abun2 %>% 
  ggplot(aes(y = All_herbs, x = Depth_m)) +
  geom_point() +
  geom_smooth()

# histogram
abun2 %>% ggplot(aes(x = All_herbs)) +
  geom_histogram()
```

# Fit the model (poisson distribution)

```{r}
abun_poi_mod <- 
  glmmTMB(All_herbs ~ Depth_m + 
            (1 | Reef_2 / Site),
        family = poisson(), 
        data = abun2,
        REML = TRUE)
```

## Model validation

```{r}
abun_poi_mod %>% testUniformity()
abun_poi_mod %>% plotResiduals()
abun_poi_mod %>% testDispersion()
```

Here we can see that our fit is garbage, so we need to reevaluate our models

# Fit model 2 (negbinom)

```{r}
abun_nb_mod <- 
  glmmTMB(All_herbs ~ Depth_m + 
            (1 | Reef_2 / Site),
        family = nbinom2(), 
        data = abun2,
        REML = TRUE)
```

## Model validation

```{r}
abun_nb_mod %>% testUniformity() # qqplot
abun_nb_mod %>% plotResiduals() # residual plot
abun_nb_mod %>% testDispersion()
```

# Save / load model

```{r}
save(abun_nb_mod, file = "Model_Outputs/abun_nb_mod.RData")

load("Model_Outputs/abun_nb_mod.RData")
```

## Predictions / emmeans

```{r}
# Prepare matrix for predicted data to be stored
abun_grid <- with(abun2,
                    data.frame(Depth_m = seq(min(Depth_m),
                                             max(Depth_m),
                                             length = 100)))

# emmeans
abun_newdata <- abun_nb_mod %>% 
  emmeans(~ Depth_m, 
          at = abun_grid,
          type = 'response') %>% # change data from log to response scale
  as.data.frame()

#abun_newdata %>% head()
```

## Plot

```{r}
p_abundepth <-
abun_newdata %>% 
  ggplot(aes(y = response, x =Depth_m)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL),
              fill = "#8AA17D",
              alpha = 0.5) +
  geom_line() +
  # here add the rawdata
  geom_point(data = abun2,
             aes(y = All_herbs),
                 color = "#929FBD",
             alpha = 0.3) +
  scale_x_continuous(name = "Depth") +
  scale_y_continuous(name = "Abundance",
                     limits = c(0,50),
                     breaks = seq(0,50, by = 10)) +
  theme_classic() +
  ggtitle("a)") +
  geom_image(data = tibble(Depth_m = 70,
                            response = 45),
                            aes(image = ("Images/siganid.png")),
                            size = 0.30)
```

## Model interpretation

```{r}
abun_nb_mod %>% broom.mixed::tidy(
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = TRUE
)
```

Depth has a negative effect on abundance of herbivores. The rate of decrease is 5.2% (1 - 0.948 in the estimate) for every m change in depth. The probability of this not happening due to chance is \< 0.001 and suggest a significant effect of depth.

## Pairwise comparisons

Let us say we want to know differences in abundance between the shallowest and maximum depth and at 50 depth. We can do so with pairwise contrasts.

### Extract min and max values

```{r}
depth_comp <- abun2 %>% 
  summarise(min_depth = min(Depth_m),
            mid_depth = 50,
            max_depth = max(Depth_m)) %>% 
  unlist(use.names = FALSE) %>% # remove column names of min and max depth
  as_tibble() %>% # have them as one column
  rename(Depth_m = value) # name column as Depth_m
```

### Pairwise between shallowest and deepest depth

```{r}
# comparisons betweem min, 50m and max depth
pairwise_depth <- 
abun_nb_mod |> 
  emmeans(~ Depth_m, 
          at = depth_comp, 
          epred = TRUE) |> 
  pairs(type = "link") %>% 
  summary(infer = c(TRUE, TRUE), # return pvalue and conf
          level = 0.95) %>%
  as.tibble()
# from the shallowest to the deepest depth band, the ratio increases (greater differences in abundance)

# [inverse] comparisons from max to min depth
abun_nb_mod |> 
  emmeans(~ Depth_m, 
          at = depth_comp, 
          epred = TRUE) |> 
  pairs(rev = TRUE, 
        type = "response") %>% 
  summary(infer = c(TRUE, TRUE), # return pvalue and conf
          level = 0.95) %>%
  as.tibble()
```

### Plot

```{r}
p_abun_pairwise <-
pairwise_depth %>% 
  mutate(contrast = fct_rev(fct_inorder(contrast))) %>% # makes 2.3m the top most of the fig
ggplot(aes(y = contrast, x = estimate)) +
  geom_point() +
  geom_pointrange(aes(x = estimate, xmax = asymp.UCL, xmin = asymp.LCL)) +
  geom_vline(xintercept = 0, lty = 11, color = "red") +
  scale_x_continuous("Contrast ratio (log-scale)") +
  scale_y_discrete("") +
  ggtitle("b)") +
  theme_classic() 
```

# Combine plot

```{r}
p_final_abun <- 
p_abundepth + p_abun_pairwise 
```

# Save plot

```{r}
ggsave("Figures/Fig_Nb_Abund_Depth.jpeg",
       plot = p_final_abun,
       dpi = 300,
       height = 5,
       width = 8,
       units = "in")
```
