---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(sjPlot) # for table visualization
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2025b) investigated changes in macroalgae cover in the Bolinao-Anda Reef Complex, Philippines. To do so, we used RUV drops across a depth range of 1-60 at 4 sites. From the RUV deployment, we took one snapshot and then quantified the number of points covered by macroalgae relative to other benthic categories. 

# Read data

```{r}
ma <- read_csv("Data/macroalgae.csv", trim_ws = TRUE)
```

## Glimpse data and find columns of interest

```{r}
ma %>% glimpse()
```

We are interested in Site, Depth, Macroalgae, Total_points

## Isolate variables of interest and data preparation

```{r}
ma2 <- 
  # old dataframe
  ma %>% 
  # select relevant columns
  select(Macroalgae, 
         Depth,
         Site,
         Total_points) %>% 
  # change Site as factor
  mutate(Site = as.factor(Site),
         Depth = as.factor(Depth)) %>% 
# calculate proportional cover. binomial needs to have responses between 0 and 1
  mutate(ma_prop = Macroalgae/Total_points)
```

# Exploratory data analysis

```{r}
# scatterplot
ma2 %>% 
  ggplot(aes(y = ma_prop, x = Depth)) +
  geom_boxplot()
```

# Fit the model (binomial distribution)

```{r}
ma_binom_mod <- 
  glmmTMB(ma_prop ~ Depth +
            (1 | Site),
        weights = Total_points,
        family = binomial(), 
        data = ma2,
        REML = TRUE)
```

## Model validation

```{r}
ma_binom_mod  %>% testUniformity()
ma_binom_mod  %>% plotResiduals() 
ma_binom_mod %>% testDispersion() 
```

Shows some signs of dispersion but looks relatively minor

# Save / load model

```{r}
save(ma_binom_mod , file = "Model_Outputs/ma_binom_mod.RData")

load("Model_Outputs/ma_binom_mod.RData")
```

## Predictions / emmeans

```{r}
# grid preparation
ma_newdata <-
  ma_binom_mod  %>% 
  emmeans(~ Depth,
          type = "response") %>% 
  as.tibble()

ma_newdata %>% head()
```

## Plot

```{r}
p_ma <-
ma_newdata %>% 
  ggplot(aes(y = prob, 
             x = Depth)) +
  geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
                  position = position_dodge(0.5),
                  color = "#8AA17D") +
  scale_x_discrete(name = "Depth") +
  scale_y_continuous(name = "Proportional macroalgae cover",
                     limits = c(0,1),
                     breaks = seq(0,1, by = 0.2)) +
  theme_classic() +
  ggtitle("a)") +
  theme(legend.position = 'none')
```

## Model interpretation

```{r}
ma_binom_mod %>% broom.mixed::tidy(
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = TRUE) %>%  # in log odds ratio
  mutate(p.value = round(p.value, 2))
```

There are differences in macroalgae cover with depth. When compared to 10m (the reference group), these differences range from 58 to 82%.

## Pairwise comparisons

```{r}
pairwise_ma <- 
 ma_binom_mod |> 
  emmeans(~Depth,
          epred = TRUE) |> 
  pairs(type = "link") %>% 
  confint(level = 0.95) %>% 
  as.tibble()

pairwise_ma %>% head()
```

### Plot

```{r}
p_pairwise_ma <-
pairwise_ma  %>% 
  mutate(contrast = fct_rev(fct_inorder(contrast))) %>% 
  ggplot(aes(y = contrast, x = estimate)) +
  geom_point() +
  geom_pointrange(aes(x = estimate, xmax = asymp.UCL + SE, xmin = asymp.LCL)) +
  geom_vline(xintercept = 0, lty = 11, color = "red") +
  scale_x_continuous("Contrast ratio (log-scale)",
                     limits = c(-3, 3)) +
  scale_y_discrete("",
                   position = "right") +
  ggtitle("b) Comparisons of macroalgae among depths") +
  theme_classic() 
```

# Combine plot

```{r}
p_final_ma <- 
p_ma + p_pairwise_ma 
```

# Save plot

```{r}
ggsave("Figures/Fig_binom_ma.jpeg",
       plot = p_final_ma,
       dpi = 300,
       height = 4,
       width = 6,
       units = "in")
```
