---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Data is from Tim and colleagues (2025) and has the same descriptions as the gaussian and lognormal models so I won't be elaborating again here.

# Read data

```{r}
arnp <- read_csv("Data/arnp_fvc.csv", trim_ws = TRUE)
```

## Glimpse data and find columns of interest

```{r}
arnp  %>% glimpse()
```
We are interested in Site, Abundance, `Size est.`, `Trophic group`

## Isolate variables of interest and data preparation

```{r}
arnp2 <- 
  # old dataframe
  arnp %>% 
  # select relevant columns
  select(Year, 
         Site,
         Abundance,
         `Size est.`,
         `Trophic group`) %>% 
  # rename size est and trophic group
  rename(Length = `Size est.`,
         Trophic_group = `Trophic group`) %>% 
  # factor Trophic group, year, site
  mutate(Trophic_group = factor(Trophic_group),
         Year = factor(Year),
         Site = factor(Site)) %>% 
  # filter planktivore, herbivore, detrivore as we will only use these
  filter(
    Trophic_group %in% c(
      "Planktivore",
      "Herbivore",
      "Detritivore"
    )
  ) %>% 
  # ensures there are other trophic groups are not counted
  droplevels() 
```

# Exploratory data analysis

```{r}
# scatterplot
arnp2 %>% 
  ggplot(aes(y = Abundance, x = Year, color = Trophic_group)) +
  geom_boxplot() +
  facet_grid(~ Trophic_group) +
  theme_classic()

# histogram
arnp2 %>% ggplot(aes(x = Abundance)) +
  geom_histogram()
```

# Fit the model (poisson distribution)

```{r}
arnp_poi_mod <- 
  glmmTMB(Abundance ~ Year * Trophic_group + 
            (1 | Site),
        family = poisson(), 
        data = arnp2,
        REML = TRUE)
```

## Model validation

```{r}
arnp_poi_mod %>% testUniformity()
arnp_poi_mod %>% plotResiduals()
arnp_poi_mod %>% testDispersion()
```

Here we can see that our fit is garbage, so we need to reevaluate our models

# Fit model 2 (negbinom)

```{r}
arnp_nb_mod <- 
  glmmTMB(Abundance ~ Year * Trophic_group + 
            (1 | Site),
        family = nbinom2(), 
        data = arnp2,
        REML = TRUE)
```

## Model validation

```{r}
arnp_nb_mod %>% testUniformity() # qqplot
arnp_nb_mod %>% plotResiduals() # residual plot
arnp_nb_mod %>% testDispersion()
```

# Fit model 3 (zero inflated)

```{r}
arnp_znb_mod <- 
  glmmTMB(Abundance ~ Length + 
            (1 | Site),
        ziformula = ~ Year + Trophic_group,
        family = nbinom2(), 
        data = arnp2,
        REML = TRUE)
```

## Model validation

```{r}
arnp_znb_mod %>% testUniformity() # qqplot
arnp_znb_mod %>% plotResiduals() # residual plot
arnp_znb_mod %>% testDispersion()
```

# AIC model comparisons

```{r}
AIC(arnp_poi_mod, arnp_nb_mod, arnp_znb_mod) %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("Model") %>% 
  arrange(AIC)
```

Model 2 seems to be the best

# Save / load model

```{r}
save(arnp_nb_mod, file = "Model_Outputs/arnp_nb_mod.RData")

load("Model_Outputs/arnp_nb_mod.RData")
```

## Predictions / emmeans

```{r}
# Prepare matrix for predicted data to be stored
# grid preparation
arnp_newdata <-
  arnp_nb_mod %>% 
  emmeans(~ Year | Trophic_group,
          type = "response") %>% 
  as.tibble()

arnp_newdata %>% head()
```

## Plot

```{r}
p_arn_abun <-
arnp_newdata %>% 
    ggplot(aes(y = response, 
             x = Year, 
             fill = Trophic_group, 
             color = Trophic_group,
             shape = Trophic_group)) +
  geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
                  position = position_dodge(0.5)) +
  facet_grid(~ Trophic_group) +
  scale_x_discrete(name = "Year") +
  scale_y_continuous(name = "Abundance",
                     limits = c(0,30),
                     breaks = seq(0,30, by = 10)) +
  theme_classic() +
  ggtitle("a)") +
  theme(legend.position = "none")
```

## Model interpretation

```{r}
arnp_nb_mod %>% broom.mixed::tidy(
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = TRUE) %>%  
  mutate(p.value = round(p.value, 2))
```

There is an interaction term, therefore we cannot interpret the year or trophic group effects by themselves. 

## Pairwise comparisons

### Pairwise between year and trophic group

```{r}
pairwise_arnp <- 
 arnp_nb_mod |> 
  emmeans(~ Year | Trophic_group, # contrast by year for each trophic group
          epred = TRUE) |> 
  pairs(type = "link") %>% 
  #pairs(type = "response") %>%
  summary(infer = c(TRUE, TRUE), # return pvalue and conf
          level = 0.95) %>%
  as.tibble()

#pairwise_arnp %>% filter(p.value < 0.05)
```
Note: interpretation on the response scale 

For herbivores, comparisons between 2016 and 2019 suggested a 23% increase in abundance, while there were no differences between 2016 and 2018. For planktivores, abundance was 62-69% greater in 2019 compared to 2016 and 2018. There were no differences in abundance between years for detritivores. 

### Plot

```{r}
p_arnp_pairwise <-
pairwise_arnp %>% 
  mutate(contrast = fct_rev(fct_inorder(contrast))) %>%
ggplot(aes(y = contrast, x = estimate, color = Trophic_group)) +
  geom_point() +
  geom_pointrange(aes(x = estimate, xmax = asymp.UCL, xmin = asymp.LCL)) +
  geom_vline(xintercept = 0, lty = 11, color = "red") +
  facet_grid(~ Trophic_group) +
  scale_x_continuous("Contrast ratio (log-scale)") +
  scale_y_discrete("", position = "right") +
  ggtitle("b)") +
  theme_classic() +
  theme(legend.position = "none")
```

# Combine plot

```{r}
p_final_arnp <- 
p_arn_abun / p_arnp_pairwise
```

# Save plot

```{r}
ggsave("Figures/Fig_Nb_Abund_ARNP.jpeg",
       plot = p_final_arnp ,
       dpi = 300,
       height = 6,
       width = 6,
       units = "in")
```