---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2019) investigated differences in the attached of Porites coral nubbins when exposed to two herbivore grazers and two butterflyfish facultative corralivores in aquaria. Coral nubbins were attached to tiles with 10 nubbins for each tile. These tiles were then exposed to the grazers or corallivores in the aquaria for 8h. The initial and final number of coral nubbins attached after 8h were then compared.

# Read data

```{r}
nub <- read_csv("Data/herb_nubbins.csv", trim_ws = TRUE)
```

## Glimpse data and find columns of interest

```{r}
nub  %>% glimpse()
```

We are interested in Fish_species, Nubbins_start, Nubbins_end, Fish_ind

## Isolate variables of interest and data preparation

```{r}
nub2 <- 
  # old dataframe
  nub %>% 
  # select relevant columns
  select(Fish_species, 
         Nubbins_start,
         Nubbins_end,
         Fish_ind) %>% 
  # change Fish_species, Fish_ind as factors
  mutate(Fish_species = as.factor(Fish_species),
         Fish_ind = as.factor(Fish_ind)) %>% 
  # abbreviate fish names
  mutate(Fish_species = recode(Fish_species,
                               "Chaetodon kleinii" = "C. kle",
      "Chaetodon lunulatus" = "C. lun",
      "Chlorurus sordidus" = "C. sor",
      "Siganus fuscescens" = "S. fus")) %>% 
  # calculate survivar probability. binomial needs to have responses between 0 and 1
  mutate(nubatt_prop = Nubbins_end/Nubbins_start)
  
```

# Exploratory data analysis

```{r}
# scatterplot
nub2 %>% 
  ggplot(aes(y = nubatt_prop, x = Fish_species)) +
  geom_boxplot() +
  theme_classic()
```

Nubbin detachment greater for grazers than butterflyfishes

# Fit the model (binomial distribution)

```{r}
herb_binom_mod <- 
  glmmTMB(nubatt_prop ~ Fish_species +
            (1 | Fish_ind),
        weights = Nubbins_start,
        family = binomial(), 
        data = nub2,
        REML = TRUE)
```

## Model validation

```{r}
herb_binom_mod  %>% testUniformity()
herb_binom_mod  %>% plotResiduals() # some minor issues with residuals
herb_binom_mod %>% testDispersion() # show signs of overdispersion
```

Fit garbage. Let's try betabinomial

# Fit model 2 (beta binomial)

```{r}
herb_bbinom_mod <- 
  glmmTMB(nubatt_prop ~ Fish_species +
            (1 | Fish_ind),
        weights = Nubbins_start,
        family = betabinomial(), 
        data = nub2,
        REML = TRUE)
```

## Model validation

```{r}
herb_bbinom_mod %>% testUniformity() # qqplot
herb_bbinom_mod %>% plotResiduals() # residual plot
herb_bbinom_mod %>% testDispersion()
```

Slight dispersion but doesn't seem too bad

# Save / load model

```{r}
save(herb_bbinom_mod, file = "Model_Outputs/herb_bbinom_mod.RData")

load("Model_Outputs/herb_bbinom_mod.RData")
```

## Predictions / emmeans

```{r}
# grid preparation
nub_newdata <-
  herb_bbinom_mod %>% 
  emmeans(~ Fish_species,
          type = "response") %>% 
  as.tibble()

nub_newdata %>% head()
```

## Plot

```{r}
p_nub <-
nub_newdata %>% 
  ggplot(aes(y = prob, 
             x = Fish_species, 
             fill = Fish_species, 
             color = Fish_species,
             shape = Fish_species)) +
  geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
                  position = position_dodge(0.5)) +
  scale_x_discrete(name = "Fish species") +
  scale_y_continuous(name = "Proportional nubbin attachment",
                     limits = c(0.8,1),
                     breaks = seq(0.8,1, by = 0.1)) +
  theme_classic() +
  ggtitle("a)") +
  theme(legend.position = 'none')
```

## Model interpretation

```{r}
 herb_bbinom_mod %>% broom.mixed::tidy(
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = TRUE) %>%  # in log odds ratio
  mutate(p.value = round(p.value, 2))
```

Nubbin detachment differs only between C. kleinii (ref group) and C. sordidus wherein attachment of nubbins in aquaria with C. sordidus is 56% lower.

## Pairwise comparisons

Let us say we want to know differences in attachment between species (i.e. not only against the reference group of C. kleinii)

### Pairwise between fish species on similar larvae

```{r}
pairwise_nub <- 
 herb_bbinom_mod |> 
  emmeans(~Fish_species,
          epred = TRUE) |> 
  pairs(type = "link") %>% 
  summary(infer = c(TRUE, TRUE), # return pvalue and conf
          level = 0.95) %>%
  as.tibble()

pairwise_nub %>% head()
```

### Plot

```{r}
p_pairwise_nub <-
pairwise_nub  %>% 
  mutate(contrast = fct_rev(fct_inorder(contrast))) %>% 
  ggplot(aes(y = contrast, x = estimate)) +
  geom_point() +
  geom_pointrange(aes(x = estimate, xmax = asymp.UCL + SE, xmin = asymp.LCL)) +
  geom_vline(xintercept = 0, lty = 11, color = "red") +
  scale_x_continuous("Contrast ratio (log-scale)",
                     limits = c(-5, 5)) +
  scale_y_discrete("",
                   position = "right") +
  ggtitle("b) Comparisons among fish species") +
  theme_classic() 
```

# Combine plot

```{r}
p_final_nub <- 
p_nub + p_pairwise_nub 
```

# Save plot

```{r}
ggsave("Figures/Fig_betabinom_Nub.jpeg",
       plot = p_final_nub,
       dpi = 300,
       height = 4,
       width = 6,
       units = "in")
```
