---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(vegan) # for multivariate analysis
library(patchwork) # for combining plots
library(ggrepel) # for multivariate plotting
library(ggforce) # for multivariate plotting
library(pairwiseAdonis) # pairwise permanova
```

# Scenario

# Read data

```{r}
tbc <- read_csv("Data/tile_benthic_composition.csv", trim_ws = TRUE)
```

## Glimpse data and find columns of interestGlimpse data and find columns of interest

```{r}
tbc %>% glimpse()
```
We are interested in Site and columns from BT to SPO

## Isolate variables of interest and data preparation

```{r}
tbc2 <- 
  # old dataframe
  tbc %>% 
  # filter only Top orientation
  filter(Orientation == "Top") %>% 
  # select relevant columns
  select(Site,
         Rep,
         BT: SPO) %>% 
  # change Site as factor
  mutate(Site = factor(Site,
                    levels = c("Tomasa",
                    "Lucero",
                    "Malilnep")))

  tbc %>% head()
```

## Separate explanatory and response matrix

```{r}
# explanatory variable
exp <- tbc %>% 
  select(Site, Rep) %>% 
  as.data.frame()

# response variable
res <- tbc %>% 
  select(BT: SPO)  %>% 
  as.data.frame()
```


## Data (response) standardization

```{r}
res_stand <- wisconsin(res^0.25)
```

data is wisconsin and fourth root transformed

# Run mds

```{r}
res_mds <- metaMDS(res_stand,
                  # distance is bray-curtis
                  distance = "bray", 
                  # number of dimensions - 2 dimensional
                  k = 2,
                  # iterations
                  try = 100,
                  # do not transform as already standardized
                  autotransform = FALSE)
```

## stressplot 

```{r}
res_mds$stress
# stress at 0.18
```

## Extract scores

```{r}
# extract scores from nmds; sites here are the individual tiles
scores_res <- as.data.frame(scores(res_mds, display = "sites"))

# create sample ID column for response matrix
scores_res$SampleID <- rownames(scores_res)

# create sample ID column for explanatory matrix
exp$SampleID <- rownames(exp)

# combine response and explanatory matrix; joined by sample id column
scores_df <- left_join(scores_res, exp, by = "SampleID")
```

## Plot

```{r}
p_nmds_tile <-
ggplot() +
  # points
  geom_point(data = scores_df,
             aes(NMDS1, NMDS2,
                 colour = Site,
                 shape = Site),
             size = 5) +
  # group ellipses for ease of visualization
  stat_ellipse(data = scores_df,
               aes(NMDS1, NMDS2, fill = Site),
               geom = "polygon",
               alpha = 0.2,
               level = 0.68) +
  # vertical and horizontal lines
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  # add nmds stress to the plot
  annotate(
    "text",
    x = 1,
    y = 1.1,
    label = paste0("Stress = ", round(res_mds$stress, 2)),
    hjust = 1.1,
    vjust = 1.5,
    size = 5
  ) +
  theme_classic()
```

Visually, there are differences in benthic composition among tiles, with Lucero different from Malilnep and Tomasa. 

# Run PERMANOVA

```{r}
adonis2(res_stand ~ 
          Site,
        data = exp,
        perm = 3000, # usually permutations are ~ 10,000 but to save time, am setting it to 3000
        strata = exp$Rep) # controls for variation with reps in a site
```

Site influenced benthic composition and explains 28% of the variance. 

## Pairwise comparisons

```{r}
pairwise_tbc <- pairwise.adonis2(
  res_stand ~ Site,
  data = exp,
  nperm = 3000,
  strata = "Rep"
)
```

All sites are significantly different, with greater variation between Lucero and Malilnep and Tomasa compared to Malilnep and Tomasa.

## Model checks

```{r}
disper <- betadisper(vegdist(res_stand, method = "bray"),
                     group = exp$Site)

permutest(disper, permutations = 3000)
```
Non-significant site effect. This suggest that any differences recorded in permanova was due to community/centroid variation rather than among site variability. 

# Run envfit

## Select only CCA, TA, BT for ease of plotting

```{r}
res_stand2 <- res_stand %>% select(CCA, TA, BT)
```

## Envfit

```{r}
res_envfit <- envfit(res_mds, 
                     env = res_stand2,
                     permutations = 3000)
```

All 3 variables were significant influential to variation in tile community explaining 54 to 68% of the variance. 

## Save envfit variables for plotting

```{r}
# extract envfit scores 
envfit_df <- as.data.frame(scores(res_envfit, display = "vectors"))

# Add variable names as a column
envfit_df$Variable <- rownames(envfit_df)
```


## Plot

```{r}
p_final_nmds <-
p_nmds_tile +
  # plots vectors
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_segment(data = envfit_df,
               aes(x = 0, y = 0,
                   xend = NMDS1,
                   yend = NMDS2),
               arrow = arrow(length = unit(0.2, "cm")),
               colour = "black",
               linewidth = 0.8) +
  # add texts
  ggrepel::geom_text_repel(
    data = envfit_df,
    aes(x = NMDS1, y = NMDS2, label = Variable),
    colour = "black",
    size = 8,
    box.padding = 0.10,
    point.padding = 0.05,
    segment.colour = NA
  )
  
```

# Save plot

```{r}
ggsave("Figures/p_final_nmds.jpeg",
       plot = p_final_nmds,
       dpi = 300,
       height = 5,
       width = 5,
       units = "in")
```
