---
title: "Sprich"
format: html
editor: visual
---

Quarto document for fitting species richness among depth bands and slope orientation using Bayesian and lognormal distribution. Habitat type and site are considered group level variables.

# Load library

```{r}
#| label: libraries
#| output: false
#| eval: true
#| warning: false
#| message: false
#| cache: false

library(tidyverse)
library(brms)
library(coda)
library(bayesplot)
library(DHARMa)
library(emmeans)
library(broom)
library(tidybayes)
library(broom.mixed)
library(bayestestR)
library(patchwork)
source("helperFunctions.R")
```

# Read data

```{r}
abun <- read_csv("Data/herb_abundance.csv",
                      trim_ws = TRUE)
glimpse(abun)
```

# Declare factors

```{r}
abun2 <- 
  # old dataframe
  abun %>% 
  # select relevant columns
  select(Reef_2, 
         Site,
         Depth_m,
         cropper,
         browser,
         detritivore,
         excavator,
         scraper) %>% 
  # change Reef_2, Site as factors
  mutate(Reef_2 = as.factor(Reef_2),
         Site = as.factor(Site)) %>% 
  # combine all herbivore feeding groups as "All_herbs"
  mutate(All_herbs = cropper + browser + detritivore + excavator + scraper)
```

# Model fitting

Not gonna run full model cause it will take too long.

## Define formula

```{r}
herbs_form <- 
  bf(All_herbs ~ 
       Depth_m +
       (1 | Site),
     family = negbinomial(link = "log"))
```

## Data exploration

```{r}
abun2 |> 
  summarise(log_med = log(median(All_herbs)),
            log_mad = log(mad(All_herbs))) 
```

## Weakly informative priors

```{r}
herb_priors <- prior(normal(1.2, 2), class = "Intercept") +
  prior(normal(0, 1), class = "b") +
  prior(gamma(0.01, 0.01), class = "shape") +
  prior(student_t(3, 0, 2), class = "sd")
```

## Prior only model

```{r}
#| cache: true
herbs_prior_mod <- brm(herbs_form,
                    data = abun2,
                    prior = herb_priors,
                    sample_prior = "only",
                    iter = 2000, # small number of iter cause too long
                    warmup = 500,
                    chains = 3,
                    cores = 6,
                    thin = 5,
                    seed = 123,
                    control = list(adapt_delta = 0.99,
                                   max_treedepth = 20),
                    refresh = 0)
```

## Prior evaluation

```{r}
herbs_prior_mod |> conditional_effects() |> 
  plot(points = TRUE,
       ask = FALSE,
       plot = FALSE) |> 
  wrap_plots() & 
  scale_y_log10()
```

## Fit model

```{r}
#| cache: true
herbs_mod <- update(herbs_prior_mod,
                  sample_prior = "yes",
                    iter = 3000,
                    warmup = 500,
                    refresh = 1000)
```

### Chain diagnostics

```{r}
# trace
herbs_mod |> mcmc_plot(type = "trace")
# autocorr
herbs_mod |> mcmc_plot(type = "acf_bar")

# rhat
herbs_mod |> mcmc_plot(type = "rhat_hist")

# ess
herbs_mod |> mcmc_plot(type = "neff_hist")
```

### Residuals

```{r}
herbs_resids <- make_brms_dharma_res(herbs_mod)

# qqplot
herbs_resids |> testUniformity()

# residplot
herbs_resids |> plotResiduals()

# testdisp
herbs_resids |> testDispersion()
```

#### Save model

```{r}
save(herbs_mod, file = "Model_Outputs/bayes_abun_mod.Rdata")
```

#### Load model

```{r}
load("Model_Outputs/bayes_abun_mod.RData")
```

# Plotting

## Newdata for plotting depth

```{r}
depth_newdata <- with(abun2,
                 data.frame(Depth_m = seq(min(Depth_m),
                                          max(Depth_m),
                                          length = 100)))
```

## Prep db for plotting

```{r, cache=TRUE}
herbs_depth_pred <- 
  herbs_mod |> 
  emmeans(~ Depth_m, 
          at = depth_newdata, 
          type = "response")
```

### Gather emmeans

```{r}
herbs_depth_pred_draws <- 
gather_emmeans_draws(herbs_depth_pred)
```

### Subset 200 draws

```{r}
herbs_depth_pred_draws_subset <- sample(unique(herbs_depth_pred_draws$.draw), 200)

herbs_depth_pred_draws_200 <- herbs_depth_pred_draws  |>  
  filter(.draw %in% herbs_depth_pred_draws_subset)
```

### Plot

```{r}
p_sprich_depth <-
herbs_depth_pred_draws_200 |> 
  ggplot(aes(x = Depth_m, 
             y = .value)) +
 geom_line(aes(group = .draw), 
            color = "#DDD487", 
            alpha = 0.25, 
            size = 1) +
   stat_lineribbon(colour = "yellow4", 
                  size = 1.5, 
                  point_interval = "median_hdci", 
                  fill = "yellow4", 
                  .width = 0.001, 
                  alpha = 1) + 
  scale_x_continuous("Depth") +
  scale_y_continuous("Abundance") +
  theme_classic()
```

# Model interpretation

## Exceedance probability

```{r}
herbs_mod |> as_draws_df() |> 
  dplyr::select(matches("^b_.*")) |> 
  exp() |> # backtransform from logscale
  summarise_draws(median,
                  HDInterval::hdi,
                  Pl= ~mean(.x < 1), #exceedence prob
                  Pg = ~mean(.x > 1)) |> 
  filter(Pl > 0.85 | # filter weak evidence (0.85)
           Pg > 0.85)
```
