---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(sjPlot) # for table visualization
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2025a) investigated changes in species richness with depth in the Coral Sea, Australia. To do so, we used ROV surveys across a depth range of 2-98 throughout 50 sites. Each ROV survey lasted for 2.5 mins and covered an estimated area of about 30m per survey.

# Read data

```{r}

```

## Glimpse data and find columns of interest

```{r}

```

We are interested in Site, Depth_m, Estimator

## Isolate variables of interest and data preparation

```{r}

```

# Exploratory data analysis

```{r}

```

# Fit the model 1


```{r}

```

## Model validation

```{r}

```


# Fit the model 2 


```{r}

```

## Model validation

```{r}

```

Now let's try including a random variable (i.e. a glmm before we )

# Fit model 3 (include site as random variable)

```{r}

```

## Model validation

```{r}

```

# Save / load model

```{r}

```

## Predictions / emmeans

```{r}

```

## Plot

```{r}

```

## Model interpretation

```{r}

```


## Pairwise comparisons

Let us say we want to know differences in species richness between the shallowest and maximum depth. We can do so with pairwise contrasts.

### Extract min and max values

```{r}

```

### Pairwise between shallowest and deepest depth

```{r}

```

### Plot

```{r}

```

# Combine plot

```{r}

```

# Save plot

```{r}

```
