---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2020) investigated changes in the settlement of Pocillopora larvae when provided tiles conditioned at different sites with varying distances form fish farms (i.e. Tomasa - near, Lucero - middle, Malilnep - far) in the Bolinao-Anda Reef Complex. We also examined nutrient concentrations of 4 nutrients (nitrite, nitrate, phosphate, ammonia) throughout those sites.

For the purposes of this exercise, we will only look at changes in phosphate concentrations with site.

# Read data

```{r}

```

## Glimpse data and find columns of interest

```{r}

```

## Isolate variables of interest and data preparation

```{r}

```

# Exploratory data analysis

```{r}

```

# Fit the model 

This assumes no site level variance (i.e. a simple glm)

```{r}

```

## Model validation

```{r}

```

# Save / load model

```{r}

```

## Predictions / emmeans

```{r}

```

## Plot

```{r}

```

## Model interpretation

```{r}

```

## Pairwise comparisons

```{r}

```

### Plot

```{r}

```

# Combine plot

```{r}

```

# Save plot

```{r}

```
