---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(sjPlot) # for table visualization
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2025) investigated changes in herbivore assemblages with depth in the Coral Sea, Australia. To do so, we used ROV surveys across a depth range of 2-98 throughout 50 sites. Each ROV survey lasted for 2.5 mins and covered an estimated area of about 30m per survey. During each survey, we identified the species, counted the abundance and estimated the size of herbivorous fishes.

For the purpose of this exercise, we will only examine changes in species richness with depth.

# Read data

```{r}

```

## Glimpse data and find columns of interest

```{r}

```

## Isolate variables of interest and data preparation

```{r}

```

# Exploratory data analysis

```{r}

```

# Fit the model 1 

```{r}

```

## Model validation

```{r}

```

# Fit the model 2 

```{r}

```

## Model validation

```{r}

```

# Fit model 3 

```{r}

```

## Model validation

```{r}

```

# Save / load model

```{r}

```

## Predictions / emmeans

```{r}

```

## Plot

```{r}

```

## Model interpretation

```{r}

```

## Pairwise comparisons

### Extract min and max values

```{r}

```

### Pairwise between shallowest and deepest depth

```{r}

```

### Plot

```{r}

```

# Combine plot

```{r}

```

# Save plot

```{r}

```
