---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(sjPlot) # for table visualization
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2025b) investigated changes in macroalgae cover in the Bolinao-Anda Reef Complex, Philippines. To do so, we used RUV drops across a depth range of 1-60 at 4 sites. From the RUV deployment, we took one snapshot and then quantified the number of points covered by macroalgae relative to other benthic categories. 

# Read data

```{r}

```

## Glimpse data and find columns of interest

```{r}

```

We are interested in Site, Depth, Macroalgae, Total_points

## Isolate variables of interest and data preparation

```{r}

```

# Exploratory data analysis

```{r}

```

# Fit the model (binomial distribution)

```{r}

```

## Model validation

```{r}

```

Shows some signs of dispersion but looks relatively minor

# Save / load model

```{r}

```

## Predictions / emmeans

```{r}

```

## Plot

```{r}

```

## Model interpretation

```{r}

```


## Pairwise comparisons

```{r}

```

### Plot

```{r}

```

# Combine plot

```{r}

```

# Save plot

```{r}

```
