---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(sjPlot) # for table visualization
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2025b) investigated changes browser assemblages and bite rates across four depth bands (1-10, 11-20, 31-40, 41-50m) and four sites in the Bolinao-Anda Reef Complex, Philippines. We also quantified changes in macroalgae cover with depth band. To quantify macroalgae cover, photographs from RUV drops (video cameras with weights) were extracted, with the photo quantified point intercept by determining the number of points intercepted by macroalgae relative to other benthic categories.

For the purpose of this exercise, we will only be looking at changes in macroalgae cover with depth band.

# Read data

```{r}

```

## Glimpse data and find columns of interest

```{r}

```

## Isolate variables of interest and data preparation

```{r}

```

# Exploratory data analysis

```{r}

```

# Fit the model (binomial distribution)

```{r}

```

## Model validation

```{r}
 
```

# Save / load model

```{r}

```

## Predictions / emmeans

```{r}

```

## Plot

```{r}

```

## Model interpretation

```{r}

```

## Pairwise comparisons

```{r}

```

### Plot

```{r}

```

# Combine plot

```{r}

```

# Save plot

```{r}

```
