---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(broom.mixed) # for tidy model interpretation
library(emmeans) # estimating marginal means
library(DHARMa) # model diagnostics
library(glmmTMB) # running glmms
library(ggimage) # for adding images
library(patchwork) # for combining plots
```

# Scenario

Tim and colleagues (2019) investigated differences in the proportion of Porites coral nubbins attached to tiles when exposed to two herbivore grazers and two butterflyfish facultative coralivores in aquaria. Ten coral nubbins were attached to each individual tile and were placed in an aquarium with a single individual of Chlorurus (grazer), Siganus (grazer) or Chaetodon (corallivores), with the fish allowed to interact with the coral nubbin for 8h. The initial (prior to the start) and final number (end) of coral nubbins attached after 8h were then compared.

# Read data

```{r}

```

## Glimpse data and find columns of interest

```{r}

```

## Isolate variables of interest and data preparation

```{r}

```

# Exploratory data analysis

```{r}

```

# Fit the model (binomial distribution)

```{r}

```

## Model validation

```{r}

```

# Fit model 2 

```{r}

```

## Model validation

```{r}

```

# Save / load model

```{r}

```

## Predictions / emmeans

```{r}

```

## Plot

```{r}

```

## Model interpretation

```{r}

```

## Pairwise comparisons

### Pairwise between fish species on similar larvae

```{r}

```

### Plot

```{r}

```

# Combine plot

```{r}

```

# Save plot

```{r}

```
