---
title: "Untitled"
format: html
editor: visual
---

# Load library

```{r}
library(tidyverse) # data manipulation
library(vegan) # for multivariate analysis
library(patchwork) # for combining plots
library(ggrepel) # for multivariate plotting
library(ggforce) # for multivariate plotting
library(pairwiseAdonis) # pairwise permanova
```

# Scenario

Tim and colleagues (2018) investigated differences in fish species assemblages across 3 geographic locations (Apo Reef, Patnanungan, Abra de Ilog) and at 3 depths (10m, 20m, 30m) in the Philippines. Fish data was obtained by conducting fish visual census throughout the geographic locations.

# Read data

```{r}

```

## Glimpse data and find columns of interest

```{r}

```

## Isolate variables of interest and data preparation

```{r}

```

## Separate explanatory and response matrix

```{r}

```

## Data (response) standardization

```{r}

```

# Run mds

```{r}

```

## stressplot

```{r}

```

## Extract scores

```{r}

```

## Plot

```{r}

```

# Run PERMANOVA

```{r}

```

## Model checks

```{r}

```

## Pairwise comparisons

```{r}

```

# Run envfit

```{r}

```

## Extract r and p values

```{r}

```

## Plot

```{r}

```

# Save plot

```{r}

```
